\documentclass{article}

\usepackage[top=1in,bottom=1in,left=1in,right=1in]{geometry}

\title{Procedure for Local Topo-based Map Exploration}
\author{Collin Johnson}

\begin{document}

\maketitle

\section{Required Files}

Before the map exploration can be successful, pull all necessary maps from woodstock using rsync in the Vulcan root 
directory:

\begin{verbatim}
  ~/Vulcan/:rsync -ravz user@woodstock.eecs.umich.edu:/data/vulcan/data/ data/
\end{verbatim}

\section{Procedure}

\begin{enumerate}
  \item Drive the robot to the starting location:
    \begin{itemize}
     \item BBB3 : in front of the elevator, facing the spiral stairs
     \item EECS3 : in front of the service elevator, facing the wall
    \end{itemize}
  \item Run \emph{start\_all\_sensors}
  \item Run \emph{start\_\{bbb3,eecs3\}\_exploration}
  \item Run \emph{log\_sensor\_data 'map name\_date.log'}
  \item Run \emph{log\_mpepc\_data mpepc\_'map name\_date.log'}
  \item Send relocalization message from DebugUI to get started. The maps are in data/campus\_maps/. Use either 
bbb3\_ground\_truth.gmm or eecs3\_ground\_truth.gmm.
  \item Jiggle the joystick a bit until relocalization is complete (should be fast).
  \item The wheelchair will start driving.
  \item Monitor progress using Exploration tab on DebugUI.
  \item Stop logging data once the robot has returned to the initial location.
\end{enumerate}

\subsection{Known Issues:}

The following are known issues with the exploration process. Fixing them is currently underway.

\begin{itemize}
  \item Currently the DebugUI will crash after the last area is explored. The robot will drive back to the starting 
location before finishing. Look at the console running \emph{map\_exploration} to see when it has finished.
  \item Area transitions are not always detected at the moment. As a result, the robot may visit some places multiple 
times, but it'll be okay. If the current area isn't detect, you can restart \emph{local\_topo\_hssh} to force an area 
detection if you want to end fast.
\end{itemize}


\section{Data}

The data logs for for exploration contain the following:

\begin{itemize}
 \item Front laser at 40Hz
 \item Back laser at 40Hz
 \item IMU at 100Hz
 \item Odometry at 125Hz
 \item Encoder data at 125Hz
\end{itemize}

\end{document}
